MS_data_clean

### 2021-10-15 MS_data_modeling/MS_data_explore.Rmd
Defines odd bees (both directions)

compare_df <- compare_df %>% merge(fowler %>% rename(specialistFOWLER = specialist) %>% 
                                     select(interestBee, specialistFOWLER), by = c('interestBee'), all = T) %>% unique() %>%
  mutate(existsGLOBEE = ifelse(is.na(degreeGLOBEE), 0, 1), existsMS = ifelse(is.na(degreeMS), 0, 1), 
         existsFOWLER = ifelse(is.na(specialistFOWLER), 0, 1),
         existsALL = existsGLOBEE*existsMS*existsFOWLER,
         specialistFOWLER = ifelse(is.na(specialistFOWLER), 0 , specialistFOWLER),
         pollenHostGLOBEE = str_to_title(pollenHostGLOBEE)) %>% rename(pollenHostsMS = pollenHosts,
                                                                                              ReferencesMS = References) %>%
  select(interestBee, specializationMS, degreeGLOBEE, degreeGLOBEE_C5, degreeGLOBEE_T, specialistFOWLER, 
         existsGLOBEE, existsMS, existsFOWLER, existsALL, pollenHostsMS, pollenHostGLOBEE, ReferencesMS)

compare_df %>% filter(existsALL == 1)
```

@@

```{r}
compare_df %>% filter(existsALL == 1) %>% group_by(specializationMS) %>% summarize('Mean GLOBI Degree'  = mean(degreeGLOBEE),
                                                                                   'GLOBI Degree IQR' = paste('[', round(quantile(degreeGLOBEE, 0.25),
                                                                                                                         2), 
                                                                                                                  ',', round(quantile(degreeGLOBEE, 0.75), 2),
                                                                                                            ']'),
                                                                                   'Mean GLOBI C5 Degree' = mean(degreeGLOBEE_C5),
                                                                                   'GLOBI C5 Degree IQR' = paste('[', round(quantile(degreeGLOBEE_C5, 0.25), 2),
                                                                                                                  ',', round(quantile(degreeGLOBEE_C5, 0.75), 2),
                                                                                                            ']'),
                                                                                   'Mean GLOBI T Degree' = mean(degreeGLOBEE_T),
                                                                                   'GLOBI T Degree IQR' = paste('[', round(quantile(degreeGLOBEE_T, 0.25), 2),
                                                                                                                  ',', round(quantile(degreeGLOBEE_T, 0.75), 2),
                                                                                                            ']'),
                                                                                   'Mean MS Degree' = mean(degreeMS),
                                                                                   'MS Degree IQR' = paste('[', round(quantile(degreeMS, 0.25), 2), 
                                                                                                                  ',', round(quantile(degreeMS, 0.75), 2),
                                                                                                            ']'),
                                                                                   'Percent Fowler Specialist' = mean(specialistFOWLER)
) %>% kbl(caption = 'Plant Family Degrees by MS Specialization') %>%
  kable_styling()
```

@@

compare_df %>% filter(specialistFOWLER == 1, specializationMS  == 'Polylectic') %>% 
  select(interestBee, specializationMS, specialistFOWLER, degreeGLOBEE_C5, degreeGLOBEE, pollenHosts) %>% filter(degreeGLOBEE_C5 > 3)
```

@@

compare_df %>% filter(specialistFOWLER == 0, specializationMS  != 'Polylectic') %>% 
  select(interestBee, specializationMS, specialistFOWLER, degreeGLOBEE_C5, degreeGLOBEE) %>% filter(degreeGLOBEE_C5 > 5)
```

@@

```{r}
compare_df
```

>>>>

compare_df <- compare_df %>% merge(fowler %>% rename(specialistFOWLER = specialist) %>% 
                                     select(interestBee, specialistFOWLER), by = c('interestBee'), all = T) %>% unique() %>%
  mutate(existsGLOBEE = ifelse(is.na(degreeGLOBEE), 0, 1), existsMS = ifelse(is.na(degreeMS), 0, 1), 
         existsFOWLER = ifelse(is.na(specialistFOWLER), 0, 1),
         existsALL = existsGLOBEE*existsMS,
         pollenHostGLOBEE = str_to_title(pollenHostGLOBEE)) %>%
  mutate(specialistFOWLER = ifelse(is.na(specialistFOWLER), 0 , specialistFOWLER))%>% 
  rename(pollenHostsMS = pollenHosts,ReferencesMS = References) %>%
  select(interestBee, specializationMS, degreeGLOBEE, degreeGLOBEE_C5, degreeGLOBEE_T, specialistFOWLER, 
         existsGLOBEE, existsMS, existsFOWLER, existsALL, pollenHostsMS, pollenHostGLOBEE, ReferencesMS, degreeMS)

compare_df %>% filter(existsALL == 0)
```

@@

```{r}
compare_df %>% filter(existsALL == 1) %>% group_by(specializationMS) %>% summarize('Mean GLOBI Degree'  = mean(degreeGLOBEE),
                                                                                   'GLOBI Degree IQR' = paste('[', round(quantile(degreeGLOBEE, 0.25),
                                                                                                                         2), 
                                                                                                                  ',', round(quantile(degreeGLOBEE, 0.75), 2),
                                                                                                            ']'),
                                                                                   'Mean GLOBI C5 Degree' = mean(degreeGLOBEE_C5),
                                                                                   'GLOBI C5 Degree IQR' = paste('[', round(quantile(degreeGLOBEE_C5, 0.25), 2),
                                                                                                                  ',', round(quantile(degreeGLOBEE_C5, 0.75), 2),
                                                                                                            ']'),
                                                                                   'Mean GLOBI T Degree' = mean(degreeGLOBEE_T),
                                                                                   'GLOBI T Degree IQR' = paste('[', round(quantile(degreeGLOBEE_T, 0.25), 2),
                                                                                                                  ',', round(quantile(degreeGLOBEE_T, 0.75), 2),
                                                                                                            ']'),
                                                                                   'Percent Fowler Specialist' = mean(specialistFOWLER)
) %>% kbl(caption = 'Plant Family Degrees by MS Specialization') %>%
  kable_styling()
```

@@

compare_df %>% filter(specialistFOWLER == 1, specializationMS  == 'Polylectic') %>% 
  select(interestBee, specializationMS, specialistFOWLER, degreeGLOBEE_C5, degreeGLOBEE, pollenHostsMS, pollenHostGLOBEE, ReferencesMS) %>% filter(degreeGLOBEE < 3)
```

@@

compare_df %>% filter(specialistFOWLER == 0, specializationMS  != 'Polylectic') %>% 
  select(interestBee, specializationMS, specialistFOWLER, degreeGLOBEE_C5, degreeGLOBEE, pollenHostsMS, pollenHostGLOBEE, ReferencesMS) %>% filter(degreeGLOBEE_C5 > 5)
```

@@
